Verifying Demonstrations

### 2017-11-15 contents-poster.tex
Improves colour coding of blocks

    \begin{blueblock}{Requirements}
      \begin{itemize}
        \item\label{EligibilityVerif} Eligibility: anyone can verify that each 
          participation proof provides temporal and spatial eligibility and that 
          it has not been counted before.

@@

@@

    \begin{block}{Designated protest}
      \begin{itemize}
        \item A protest is identified by its cause, captured in a 
          manifesto.
        \item The hash of the manifesto provides an unpredictable identifier 
          (\(cid\) in figures).
        \item It's difficult to create a second manifesto that disagrees but 
          gets the same identifier.
      \end{itemize}
    \end{block}

    \begin{block}{Privacy-preserving linkability}
      \begin{itemize}
        \item We want linkability to prevent Sybil attacks.
        \item We also want privacy.
        \item We use techniques from anonymous credentials to create identifiers 
          (\(pid, wid\) in figures).
        \item The identifiers are random but unique per protest, i.e.\ depends 
          on \(cid\).
        \item The accompanying \ac{NIZK} proof prevents cheating (used during 
          verification).
      \end{itemize}
    \end{block}

    \begin{block}{Temporal eligibility}
      \begin{itemize}
        \item We use a blockchain for commitments, freshness.
        \item Freshness: a protester must include the head (hash value) of the 
          blockchain in their proof shares (\(t_s\) in figures).
        \item This value is difficult to guess and prevents preparing proofs too 
          long in advance.
        \item Commitments: when a proof share is prepared, it is committed to 
          the blockchain for timestamping.
      \end{itemize}
    \end{block}

    \begin{block}{Location proofs and spatial eligibility}
      \begin{itemize}
        \item Each proof must be bound to the location.
        \item This is done using witnesses.
        \item A witness runs a distance-bounding protocol to ensure proximity.
        \item If in proximity, the witness will issue a witness identifier and 
          signature (\(wid, wsig\)).
      \end{itemize}
    \end{block}

\begin{block}{Verifying the participation count}

There are three parts to verifying the participation count.
First, we must verify the eligibility of each proof, i.e.\ of all its shares.
Second, we must count these valid proofs.
Third, each protester must check that their proof is indeed registered so that 
it can be counted.

\end{block}

\begin{block}{Eligibility and universal verifiability}

@@

\end{block}

\begin{block}{Individual verifiability and receipt freeness}

@@

\end{block}

>>>>

    \begin{blueblock}{Requirements for verifiability}
      \begin{itemize}
        \item\label{EligibilityVerif} Eligibility: anyone can verify that each 
          participation proof provides temporal and spatial eligibility and that 
          it has not been counted before.

@@

    \begin{blueblock}{Requirements for privacy}
      \begin{itemize}
        \item The verifiability protocol should not increase the risk already 
          incurred by attending.
      \end{itemize}
    \end{blueblock}

@@

    \begin{blackblock}{Designated protest}
      \begin{itemize}
        \item A protest is identified by its cause, captured in a 
          manifesto.
        \item The hash of the manifesto provides an unpredictable identifier 
          (\(cid\) in figures).
        \item It's difficult to create a second manifesto that disagrees but 
          gets the same identifier.
      \end{itemize}
    \end{blackblock}

    \begin{blackblock}{Privacy-preserving linkability}
      \begin{itemize}
        \item We want linkability to prevent Sybil attacks.
        \item We also want privacy.
        \item We use techniques from anonymous credentials to create identifiers 
          (\(pid, wid\) in figures).
        \item The identifiers are random but unique per protest, i.e.\ depends 
          on \(cid\).
        \item The accompanying \ac{NIZK} proof prevents cheating (used during 
          verification).
      \end{itemize}
    \end{blackblock}

    \begin{blackblock}{Temporal eligibility}
      \begin{itemize}
        \item We use a blockchain for commitments, freshness.
        \item Freshness: a protester must include the head (hash value) of the 
          blockchain in their proof shares (\(t_s\) in figures).
        \item This value is difficult to guess and prevents preparing proofs too 
          long in advance.
        \item Commitments: when a proof share is prepared, it is committed to 
          the blockchain for timestamping.
      \end{itemize}
    \end{blackblock}

    \begin{blackblock}{Location proofs and spatial eligibility}
      \begin{itemize}
        \item Each proof must be bound to the location.
        \item This is done using witnesses.
        \item A witness runs a distance-bounding protocol to ensure proximity.
        \item If in proximity, the witness will issue a witness identifier and 
          signature (\(wid, wsig\)).
      \end{itemize}
    \end{blackblock}

    \begin{blueblock}{Verifying the participation count}
      \begin{enumerate}
        \item We must verify the eligibility of each proof, i.e.\ of all its 
          shares.
        \item We must count these valid proofs.
        \item Each protester must check that their proof is indeed registered so 
          that it can be counted.
      \end{enumerate}
    \end{blueblock}

\begin{blackblock}{Eligibility and universal verifiability}

@@

\end{blackblock}

\begin{blackblock}{Individual verifiability and receipt freeness}

@@

\end{blackblock}
